{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed

### 2017-05-03 bmvc_review.tex
EnkCF2 figure removed

\begin{figure}[!t]
\centering
\begin{tabular}{cc}
\bmvaHangBox{\includegraphics[width=12.00cm]{./figures//Workflow_MKCF+PF.pdf}}\\
(a) \\
\bmvaHangBox{\includegraphics[width=10.0cm]{./figures/Workflow_EnKCF2+PF.pdf}}\\
(b)
\end{tabular}
\caption{The workflow of the proposed $\geq300$fps {\it E}nKCF tracker
  (a). It is slightly modified to handle extreme ego-motion and we
  call it the {\it E}nKCF2 tracker (b) running at $\geq100$fps.}
\label{Workflows}
\end{figure}

>>>>

\begin{figure}[!t]
\centering
\begin{tabular}{cc}
\bmvaHangBox{\includegraphics[width=12.00cm]{./figures//Workflow_MKCF+PF.pdf}}\\

\end{tabular}
\caption{The workflow of the proposed $\geq300$fps {\it E}nKCF tracker.}
\label{Workflows}
\end{figure}
